Sushi monster

### 2025-02-11 inst/sushi.Rmd
remove unnecessary packages
consistentification

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
library("partitions")
library("pdftools")
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("hyper2")
```

@@

```{r calclike, cache=TRUE}
f <- function(strength){
   H <- make_sushi_H(a[wanted,-1], strength=strength)
   maxp(H,give=1)$`Log-likelihood`
}
s <- seq(from=0.4,to=2,len=8)
L <- sapply(s,f)
```

```{r}
plot(s,L-max(L),type='b')
```
